Convolutional equivalent layer for gravity data processing

### 2020-08-09 manuscript/figures.tex
replot all figures with width 4.33 inches / 12000 dpi

\plot{synthetic_data_med}{width=13.5cm}{
	{Application to synthetic data. 
	Noise-corrupted gravity data (in color map) produced by three synthetic sources: 
	a sphere with density contrast $-1.25\, \mathrm{g/cm^3}$ and 
	two rectangular prisms with density contrasts $1.00\, \mathrm{g/cm^3}$ (upper-left body) and 
	$1.30\, \mathrm{g/cm^3}$ (upper-right body). 
	The black lines represent the horizontal projection of the sources.}
	\label{fig:synthetic_data}
}

\plot{deltas_gz_med}{width=6cm}{
	{Application to synthetic data. 
	Residuals between the simulated data (Figure \ref{fig:synthetic_data}) and 
	predicted data produced by: (a) the fast equivalent-layer technique \citep{siqueira-etal2017} and (b) our method. 
	The mean ($-4.493 \times 10^{-5}$ mGal) and standard deviation ($0.093$ mGal) for residuals shown in a and b are exactly the same.
	(c) Difference between a and b.
	The computation times spent by the fast equivalent-layer technique and 
	our method were $10.416$ s and $0.177$ s, respectively.}
	\label{fig:comparison_datafits}
}

\plot{upward_fourier_med}{width=13.5cm}{
	{Application to synthetic data.
	(a) Noise-free gravity data produced by the synthetic sources at $z = -300$ m.
	Residuals between the data shown in a and the upward-continued 
	data obtained by: (b) our method (not shown), with 
	mean $0.003$ mGal and standard deviation $0.034$ mGal, 
	(c) the fast equivalent-layer technique (not shown), with 
	mean $0.003$ mGal and standard deviation $0.034$ mGal and 
	(d) the classical Fourier approach (not shown), with 
	mean $-0.030$ mGal and standard deviation $0.262$ mGal. 
	The computation times spent by the fast equivalent-layer technique and 
	our method were $8.697$ s and $0.005$ s, respectively.}
	\label{fig:upward_comparison}
}

\plot{downward_fourier_med}{width=13.5cm}{
	{Application to synthetic data. 
	(a) Noise-free gravity data produced by the synthetic sources at $z = -50$ m.
	Residuals between the data shown in a and the downward-continued 
	data obtained by: (b) our method (not shown), with 
	mean $-0.001$ mGal and standard deviation $0.038$ mGal, 
	(c) the fast equivalent-layer technique (not shown), with 
	mean $-0.001$ mGal and standard deviation $0.038$ mGal and 
	(d) the classical Fourier approach (not shown), with 
	mean $-0.030$ mGal and standard deviation $0.262$ mGal.
	The computation times spent by the fast equivalent-layer technique and 
	our method were $8.795$ s and $0.004$ s, respectively.}
	\label{fig:downward_comparison}
}

@@

\plot{carajas_real_data}{width=13.5cm}{
	{Application to field data over the Caraj{\'a}s Province, Brazil. 
	Observed gravity data on a regular grid of $500 \times 500$ points, totaling $N = 250,000$ 
	observations. The inset shows the study area (red rectangle) which covers the southeast part of 
	the state of Par{\'a}, north of Brazil.}
	\label{fig:carajas_real_data}
}

\plot{Carajas_gz_predito}{width=8cm}{
	{Application to field data over the Caraj{\'a}s Province, Brazil. 
	(a) Predicted data produced by our method. (b) Residuals between the observed  
	(Figure \ref{fig:carajas_real_data}) and the predicted data (panel a), with mean 
	$0.000292$ mGal and standard deviation of $0.105$ mGal.}
	\label{fig:carajas_gz_predito_val}
}

\plot{up5000_carajas_500x500}{width=13.5cm}{
	{Application to field data over the Caraj{\'a}s Province, Brazil. 
	The upward-continued gravity data obtained with our method $5,000$ m above the 
	observed data (Figure \ref{fig:carajas_real_data}).
	The total computation time for processing of the $250,000$ observations was $0.216$ s.}
	\label{fig:up2000_carajas_500x500}
}

>>>>

\plot{Figure5}{width=13.5cm}{
	{Application to synthetic data. 
	Noise-corrupted gravity data (in color map) produced by three synthetic sources: 
	a sphere with density contrast $-1.25\, \mathrm{g/cm^3}$ and 
	two rectangular prisms with density contrasts $1.00\, \mathrm{g/cm^3}$ (upper-left body) and 
	$1.30\, \mathrm{g/cm^3}$ (upper-right body). 
	The black lines represent the horizontal projection of the sources.}
	\label{fig:synthetic_data}
}

\plot{Figure6}{width=6cm}{
	{Application to synthetic data. 
	Residuals between the simulated data (Figure \ref{fig:synthetic_data}) and 
	predicted data produced by: (a) the fast equivalent-layer technique \citep{siqueira-etal2017} and (b) our method. 
	The mean ($-4.493 \times 10^{-5}$ mGal) and standard deviation ($0.093$ mGal) for residuals shown in a and b are exactly the same.
	(c) Difference between a and b.
	The computation times spent by the fast equivalent-layer technique and 
	our method were $10.416$ s and $0.177$ s, respectively.}
	\label{fig:comparison_datafits}
}

\plot{Figure7}{width=13.5cm}{
	{Application to synthetic data.
	(a) Noise-free gravity data produced by the synthetic sources at $z = -300$ m.
	Residuals between the data shown in a and the upward-continued 
	data obtained by: (b) our method (not shown), with 
	mean $0.003$ mGal and standard deviation $0.034$ mGal, 
	(c) the fast equivalent-layer technique (not shown), with 
	mean $0.003$ mGal and standard deviation $0.034$ mGal and 
	(d) the classical Fourier approach (not shown), with 
	mean $-0.030$ mGal and standard deviation $0.262$ mGal. 
	The computation times spent by the fast equivalent-layer technique and 
	our method were $8.697$ s and $0.005$ s, respectively.}
	\label{fig:upward_comparison}
}

\plot{Figure8}{width=13.5cm}{
	{Application to synthetic data. 
	(a) Noise-free gravity data produced by the synthetic sources at $z = -50$ m.
	Residuals between the data shown in a and the downward-continued 
	data obtained by: (b) our method (not shown), with 
	mean $-0.001$ mGal and standard deviation $0.038$ mGal, 
	(c) the fast equivalent-layer technique (not shown), with 
	mean $-0.001$ mGal and standard deviation $0.038$ mGal and 
	(d) the classical Fourier approach (not shown), with 
	mean $-0.030$ mGal and standard deviation $0.262$ mGal.
	The computation times spent by the fast equivalent-layer technique and 
	our method were $8.795$ s and $0.004$ s, respectively.}
	\label{fig:downward_comparison}
}

@@

\plot{Figure9}{width=13.5cm}{
	{Application to field data over the Caraj{\'a}s Province, Brazil. 
	Observed gravity data on a regular grid of $500 \times 500$ points, totaling $N = 250,000$ 
	observations. The inset shows the study area (red rectangle) which covers the southeast part of 
	the state of Par{\'a}, north of Brazil.}
	\label{fig:carajas_real_data}
}

\plot{Figure10}{width=8cm}{
	{Application to field data over the Caraj{\'a}s Province, Brazil. 
	(a) Predicted data produced by our method. (b) Residuals between the observed  
	(Figure \ref{fig:carajas_real_data}) and the predicted data (panel a), with mean 
	$0.000292$ mGal and standard deviation of $0.105$ mGal.}
	\label{fig:carajas_gz_predito_val}
}

\plot{Figure11}{width=13.5cm}{
	{Application to field data over the Caraj{\'a}s Province, Brazil. 
	The upward-continued gravity data obtained with our method $5,000$ m above the 
	observed data (Figure \ref{fig:carajas_real_data}).
	The total computation time for processing of the $250,000$ observations was $0.216$ s.}
	\label{fig:up2000_carajas_500x500}
}
